Acceleration of Derivative Calculations with Application to Radial Basis Function -- Finite-Differences on the Intel MIC Architecture

### 2014-01-15 acm/ieee_paper.tex
More changes.

\def\red#1{\textbf{\textcolor{red}{#1}}}
\def\blue#1{\textbf{\textcolor{blue}{#1}}}
\def\qes#1{{\blue{*** For Erik: #1 ***}}}
\def\es#1{{\blue{*** For Erik: #1 ***}}}
\def\ge#1{{\red{#1}}}
\def\NOTE#1{{\red{*** NOTEGordon: #1 ***}}}
\def\ttt#1{{\tt #1}}
\def\bold#1{{\bf #1}}

@@

Section~\ref{sec:model} presents an
estimation of the instruction intensity of various forms of the
computations. We show that a sixfold improvement can be
expected when computing the sixteen multiplications simultaneously to
reach a total of about 210~Gflop/s. This performance represents
approximately 10\% of the available flop/s of a Xeon Phi
coprocessor. \ge{Therefore, it is necessary to have an implementation that
performs the computation in as few instructions as
possible.} \NOTE{I DO NOT FOLLOW the Therefore in the previous sentence.}
We describe in Section~\ref{sec:impl} the details of the MIC
architecture and how to use specialized load, store, swizzle and
permutation instructions to efficiently bring the data from memory into the vector
registers to be processed. Section~\ref{sec:expe} gives some
experimental results about the amount of bandwidth that can be achieved
depending on how the SpMV kernel is written. 
It also provides the actual performance of the various kernels on multiple classes of matrices, 
some generated for purpose of analysis, and some extracted from an application of RBF-FD. 
A performance of 135~Gflop/s is achieved using RBF-FD differentiation matrices. Concluding remarks and perspectives are provided in Section~\ref{sec:ccl}.\looseness=-1

>>>>

\def\red#1{\textbf{\textcolor{red}{#1}}}
\def\blue#1{\textbf{\textcolor{blue}{#1}}}
\def\qes#1{{\blue{*** For Erik: #1 ***}}}
\def\es#1{{\blue{*** For Erik: #1 ***}}}
\def\ge#1{{\blue{#1}}}
\def\NOTE#1{{\red{NOTE: #1}}}
\def\ttt#1{{\tt #1}}
\def\bold#1{{\bf #1}}

@@

Section~\ref{sec:model} presents an
estimation of the instruction intensity of various forms of the
computations. We show that a sixfold improvement can be
expected when computing the sixteen multiplications simultaneously to
reach a total of about 210~Gflop/s. This performance represents
approximately 10\% of the available flop/s of a Xeon Phi
coprocessor. \ge{Therefore, it is necessary to have an implementation that
performs the computation in as few instructions as
possible.} \NOTE{I DO NOT FOLLOW the Therefore in the previous sentence.}
\ge{We describe in Section~\ref{sec:impl} the details of the MIC
architecture and how to use specialized load, store, swizzle and
permutation instructions to efficiently bring the data from memory into the vector
registers to be processed. Section~\ref{sec:expe} presents results on 
memory access and computational speed and their relation to choices made in the 
SpMV kernels.}
%experimental results  discussing the relationship between the structure of $A$ and 
%the ; specifcally on the amount of bandwidth that can be achieved
%depending on how the SpMV kernel is written. 
It also provides the actual performance of the various kernels on multiple classes of matrices, 
some generated for purpose of analysis, and some extracted from an application of RBF-FD. 
A performance of 135~Gflop/s is achieved using RBF-FD differentiation matrices. Concluding remarks and perspectives are provided in Section~\ref{sec:ccl}.\looseness=-1
